---
title: "CI-assignment"
author: "TANG"
date: "2024-02-12"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# have a look at data
```{r}
library(readr)
df <- read.csv("framingham_assignment.csv")
```

# Week1:Formulate the research question for your assignment in two different ways.

## In words
We are asked to estimate the causal effect of cigarette smoking (CURSMOKE) on the risk of Stroke (STROKE).

## Using the potential outcome notation
Y observed outcome (dependent variable) in this case is the status of Stroke,i.e.
```{r}
Y <- df$STROKE
table(Y)
```
We can see the summary of the status of Stroke is 4019 individuals are not, while 415 individuals are in stroke situation.

X observed exposure in this case is the Variables in the dataset measured during the first examination period, which is CURSMOKE (Current cigarette smoking ,0=Not current smoker),i.e.
```{r}
X <- df$CURSMOKE
table(X)
```
We can see the summary that is 2253 individuals are not current smokers, while 2181 individuals are current smokers.

subset our observed outcome Y(STROKE) and observed exposure X(CURSMOKE) as follow:
```{r}
selected_columns <- c("RANDID", "CURSMOKE", "STROKE")
df_selected <- df[, selected_columns]
```
we can have a short overview of it:
```{r}
head(df_selected)
```

# Week2: Formulate the first 6 key items of a protocol for a target trial

## 1. Eligibility criteria
people in the community of Framingham, Massachusetts.

## 2. Exposure definition
In this study the binary exposure is serious current cigarette smoking (yes/no).

## 3. Assignment procedures
there is no randomization here.

## 4. Follow-up period
Each participant was followed for a total of 24 years.

## 5. Outcome definition
STROKE is the outcome of interest.

## 6. Causal contrast of interest
A causal contrast of interest could be E(Y(1))- E(Y(0)). As Y is binary, this is a risk difference (because E(Y(1)) = the probability that Y(1)). This is the difference between the risk of stroke within 24 years whose current status is yes versus the risk of whose current status is no.
```{r}
library(dplyr)
Y_1 <- filter(df_selected,CURSMOKE == 1)
Y_0 <- filter(df_selected,CURSMOKE == 0)
causal_contrast <- mean(Y_1$STROKE) - mean(Y_0$STROKE) 
causal_contrast
```





